Concurrent, Parallel Garbage Collection in Linear Time

### 2016-05-27 finaletd/mainabstract.tex
minor fixes

\chapter*{Abstract}
\label{ch:abstract}
Garbage collection is slowly moving from being a utility program to a requirement of every modern programming language. Manual memory management offers great control in sequential programs. With multi-cores and distributed systems, most programs written recently are heavily multi-threaded and distributed. Generally, programs were written that uses multi-threading and distributed are called concurrent programming. Concurrent programming is characterized by multiple independent processes/threads, communicate among them, the uncertain order of concurrent operations among them.

The uncertainty in the order of operations makes the manual memory management of the concurrent programs difficult. Languages like C++ offers support to manage memory using smart pointers. These smart pointers are simply reiterated garbage collection algorithm working for simple object graph in the heap. In fact, smart pointer usage does not guarantee you from memory leaks. For cyclic object graph, the concurrent process must identify that it is creating the cycle and must use the special type of smart pointer to indicate it is a cyclic object graph to help smart pointers collect garbage. Smart pointers require hints from process to avoid memory leaks. Garbage collectors can avoid all memory leaks, dangling pointers, and double deletion problems in any programming environment.

>>>>

\chapter*{Abstract}
\label{ch:abstract}
Garbage collection is moving from being a utility to a requirement of every modern programming language. Manual memory management offers great control in sequential programs\todo{why is this sentence here?}. With multi-core and distributed systems, most programs written recently are heavily multi-threaded and distributed. Distributed and multi-threaded programs are called concurrent programs. Concurrent programming is characterized by: multiple independent processes/threads, communication between processes/threads, and uncertainty in the order of concurrent operations.

The uncertainty in the order of operations makes manual memory management of concurrent programs difficult. Languages like C++ offer support for memory management using using smart pointers. Smart pointer usage does not guarantee protection from memory leaks. For cyclic object graphs, a concurrent process must identify that it is creating a cycle and must use a special type of smart pointer to close a cyclic. Smart pointers, therefore, require hints from the programmer to avoid memory leaks. General garbage collectors, on the other hand, can avoid memory leaks, dangling pointers, and double deletion problems in any programming environment without help from the programmer.
